Distributed Tic Tac Toe:\\ Peer-to-Peer Team-Based Gaming System

### 2017-12-01 paper/paper.tex
Paper - Conclusion & Future Work

\begin{abstract}
This article describes a Distributed Multiplayer Tic Tac Toe software game written in Java using the RMI API. While previous implementations attempting to serve a similar purpose exist, none of them boast good design or efficiency and neither of them deliver the same functionality. The developed piece of software allows clients to play locally or globally a game of the classic tic tac toe - but with a twist. Players are separated into teams and decide on what the next move should be by voting. The implementation is derived from a design that follows the distributed applications guidelines and is prepared to handle corner cases such as client disconnects for example.
\end{abstract}

@@

The leaders communicate the vote of their team to the opposing leader so that they may pass that result on to the peers of that team, as pictured in figure 1.

By considering the fact that only the two leaders communicate about the votes between the two teams, then the system can easily break if one of the leaders crashes.

In order to avoid that and provide a more robust system we chose to implemet the Bully Algorithm on each of the players so they will be able to detect a leader crash if they do not receive a vote reply from them in a certain period of time.

After that, they can easily call for an election on older processes than them and wait for a leader to be announced on a different period of time.

If no leader is announced on that period of time or there are no older processes, then that process can declare itself leader to the rest of the team and the opponent leader.

@@

A Game class implements GameInt and extends the UnicastRemoteObject. It is an analogy for what a player knows and does during a game. It provides an implementation for all the listed classes in the interface which include the functionality of requesting the player to make a play, setting the leader of the game, several methods to interact with the Role of the player and a main method that connects to other game instances. 
C
urrently, when running the game, the user passes it a local instance name and the name of another instance as arguments. Each instance then uses this information to do an RMI Registry lookup and get a reference to the other client. The Role interface allows the application to differentiate between Leader and Player classes which extend it.

@@

\section{Conclusions and Future Work}
%make the bully algorithm work when both leaders crash at the same time
%team balancing
%randomised moves not implemented

>>>>

\begin{abstract}
This article describes a Distributed Multiplayer Tic Tac Toe software game written in Java using the RMI API. While previous implementations attempting to serve a similar purpose exist, none of them boast good design or efficiency and neither of them deliver the same functionality. The developed piece of software allows clients to play a game of Tic Tac Toe locally - but with a twist. Players are separated into teams and decide on what the next move should be by voting. The implementation is derived from a design that follows the distributed applications guidelines and is prepared to handle corner cases such as client disconnects for example.
\end{abstract}

@@

Upon initialising the game, the player will take a note of their address and port number. As the game is played on a local network, the player will attempt to connect to any other existing nodes on the network. If none are found, then the client will initialise a new game instance and set itself as one of the leaders.

When other players attempt to check for existing players on the network and successfully find them, it will get the current game state, check if it is one of the leaders, print the board in text format and prepare for the turn.

The leaders update a common game state at the end of each event before broadcasting the game state to all team members. Players are told by the leaders when completion of the game occurs.

@@

A Game class implements GameInt and extends the UnicastRemoteObject. It is an analogy for what a player knows and does during a game. It provides an implementation for all the listed classes in the interface which include the functionality of requesting the player to make a play, setting the leader of the game, several methods to interact with the Role of the player and a main method that connects to other game instances.

Currently, when running the game, the user passes it a local instance name and the name of another instance as arguments. Each instance then uses this information to do an RMI Registry lookup and get a reference to the other client. The Role interface allows the application to differentiate between Leader and Player classes which extend it.

@@

\section{Conclusions and Future Work}
%make the bully algorithm work when both leaders crash at the same time
%team balancing
%randomised moves not implemented
The produced software serves as a good demonstration of a distributed game. The use of a simple, well known game idea turned into a distributed, multiplayer experience highlights the benefits and complexities associated with distributed systems, and allows the technology to be demonstrated in an inclusive format, allowing users of all levels to make use of the software without additional complications added.

For future additions or design reconsiderations, Distributed Tic Tac Toe could benefit from some changes. These changes include making the software more robust and granting the users an improved playing experience by addressing certain network issues and gameplay elements.

In the softwares current state, leaders are appointed using the bully algorithm when a new election is required. However, there is no support for failure of communication from both leaders, i.e. if both leaders were to crash at the same time. Although the likelihood is slim, addressing the possibility of this scenario playing out would make the system more robust and prevent frustration for the players.

To improve the gameplay experience, players of both teams should be on an even playing field. To ensure this is consistent throughout the duration of a match, some form of automatic team balancing is recommended, allowing each team to receive votes in as even amount as possible. The gameplay experience could be improved further still by addressing the scenario of an even number of votes being cast by team members. The possibility of this happening is certainly high, and the recommendation is that the leader randomly selects between the moves chosen by the team members.
